---
title: "Football Salary Exploration"
output: html_notebook
author: Kelly Rivera
---



# probability distribution

Data set: American Football: Analysis on the Salary of 5.5k Pro-Players

## Install & load libraries
```{r}
# Install tidyverse
#install.packages("tidyverse")
#install.packages("corrplot")

# load libraries
library(tidyverse)
library(ggplot2)
library(corrplot)
```

## Import Dataset CSV
```{r}
# Importing the csv file
ausWeather <- read_csv("weatherAUS.csv") %>% subset(select = c(Date, MinTemp, MaxTemp, Rainfall, WindGustDir, WindGustSpeed, RainToday,
                                                               RainTomorrow)) %>% drop_na()

ausWeather
```

## Can we predict the Max Temputature for a given day based on Min Temperature, Rainfall, and WindGustSpeed?
```{r}
# Correlation calculation
corrMatixdata <- select(ausWeather, "MaxTemp", "MinTemp", "Rainfall", "WindGustSpeed")
corrMatix <-cor(corrMatixdata)
corrplot(corrMatix, method = "number")
```

## Get training and testing sets
```{r}
# Set the random seed for repetablility
set.seed(123)

# Split the data 
sample <- sample.split(ausWeather$Date, SplitRatio = .75)
train <- subset(ausWeather, sample == TRUE)
test <- subset(ausWeather, sample == FALSE)

```

## Build model on Training Set
Given min temp, predict the max temp
```{r}
model1 <- lm(MaxTemp ~ MinTemp, data = train)
model1
```

# predict the testing set
```{r}
# Predict the psoition with the model and the test data
predictedMaxTemp1 <- predict(model1, test)
```

# Actual vs. Predicted
```{r}
tempPrediction1 <- data.frame(MinTemp = test$MinTemp,
                               ActualMaxTemp = test$MaxTemp,
                               PredictedMaxTemp = predictedMaxTemp1)
tempPrediction1
```

## Visualize the predition
```{r}
ggplot(data = tempPrediction1, mapping = aes(x = MinTemp)) +
  geom_point(mapping = aes(y = ActualMaxTemp), color = "blue") +
  geom_point(mapping = aes(y = PredictedMaxTemp), color = "red") +
  labs(title = "Predicted Max Temp. Given Min Temp.",
       subtitle = "Source: Kaggle",
       caption = "* Predicted Temp. in Red",
       y = "Max. temperature",
       x = "Min. temperature")
```

## RSME
```{r}
rmse <- RMSE(tempPrediction1$ActualMaxTemp, tempPrediction1$PredictedMaxTemp)
cat("Root Squared Mean Error", rmse)
```

----------------------------------------------------------------------------------------------------------------


## Build model on Training Set
Given Rainfall, predict the max temp
```{r}
model2 <- lm(MaxTemp ~ Rainfall, data = train)
model2
```

# predict the testing set
```{r}
# Predict the psoition with the model and the test data
predictedMaxTemp2 <- predict(model2, test)
```

# Actual vs. Predicted
```{r}
tempPrediction2 <- data.frame(Rainfall = test$Rainfall,
                               ActualMaxTemp = test$MaxTemp,
                               PredictedMaxTemp = predictedMaxTemp2)
tempPrediction2
```


## Visualize the predition
```{r}
ggplot(data = tempPrediction2, mapping = aes(x = Rainfall)) +
  geom_point(mapping = aes(y = ActualMaxTemp), color = "blue") +
  geom_point(mapping = aes(y = PredictedMaxTemp), color = "red") +
  labs(title = "Predicted Max Temp. Given Rainfall",
       subtitle = "Source: Kaggle",
       caption = "* Predicted Temp. in Red",
       y = "Max. temperature",
       x = "Rainfall")
```

## RSME
```{r}
rmse <- RMSE(tempPrediction2$ActualMaxTemp, tempPrediction2$PredictedMaxTemp)
cat("Root Squared Mean Error", rmse)
```


-------------------------------------------------------------------------------


## Build model on Training Set
Given WindGustSpeed, predict the max temp
```{r}
model3 <- lm(MaxTemp ~ WindGustSpeed, data = train)
model3
```

# predict the testing set
```{r}
# Predict the position with the model and the test data
predictedMaxTemp3 <- predict(model3, test)
```

# Actual vs. Predicted
```{r}
tempPrediction3 <- data.frame(WindGustSpeed = test$WindGustSpeed,
                               ActualMaxTemp = test$MaxTemp,
                               PredictedMaxTemp = predictedMaxTemp3)
tempPrediction3
```


## Visualize the predition
```{r}
ggplot(data = tempPrediction3, mapping = aes(x = WindGustSpeed)) +
  geom_point(mapping = aes(y = ActualMaxTemp), color = "blue") +
  geom_point(mapping = aes(y = PredictedMaxTemp), color = "red") +
  labs(title = "Predicted Max Temp. Given Wind Gust Speed",
       subtitle = "Source: Kaggle",
       caption = "* Predicted Temp. in Red",
       y = "Max. temperature",
       x = "Wind Gust Speed")
```

## RSME
```{r}
rmse <- RMSE(tempPrediction3$ActualMaxTemp, tempPrediction3$PredictedMaxTemp)
cat("Root Squared Mean Error", rmse)
```










